Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-05-06 paper/ms.tex
some edits

\begin{abstract}
We use cosmological N-body simulations to find the characteristic mass
of dark matter halos hosting Lyman-Alpha Emitting (LAE) galaxies at a
redshift of $z=3.1$. The method is based on matching the statistics
for the number density between mock and observed fields. The mock
catalogs are constructed using a simple model where the basic
principle is that a dark matter halo can only host one LAE with a
probability $f_{\rm occ}$ if its mass is found withing a certain range
mass range delimited by two threshold values, $M_{\rm min}$ and $M_{\rm max}$. We generate
hundreds of mock catalogs in a thourough exploration of the parameter
space of this model. These catalogs are constructed in such a way as o
reproduce the observed areas and spatial correlations between the
different observed fields. We find that the models that are consistent
the observed cosmic variance statistics are those with halo masses in
the range $M_{\rm  min}=$ and $M_{\rm max}=$ with and occupation
fraction that scales as $f_{\rm occ}=$ with the minimum mass. We
explore three additional constraints to narrow these range. First we
select the models with the highest possible number of mocks consistent
with observations. Second we use observational constraints on the
occupation fraction. Third, we compute the angular correlation
function in the mocks against observational values. The first two
conditions narrow down the space parameter to $M_{\rm min}=$ and
$M_{\rm max}$, $f_{\rm occ}$. Although we find that the angular
correlation function is in agreement with the observational
constraints mostly due to the cosmic variance in the small angular
fields where this statistics has been computed so far, this statistics
does not allows us to put tighter constraints on the model
parameters. We also present predictions for future measurements of the
correlation function on larger continous fields. We make available the
mock data for the best models in a public repository. Implications for
galaxy formation models? 
\end{abstract}

@@

Most models of galaxy formation find that the mass of the halo largely
determines key properties of the galaxy such as its stellar mass and
star formation rate. Processes that regulate the star formation cycle
are also though to be strongly dependent on its mass. Furthermore, the
spatial clustering of galaxies on large scales is entirely dictated by
the halo distribution.  For the reasons mentioned above, finding the
typical dark matter halo mass hosting LAEs represents a significant
step forward to understand the nature of this population in the
context of LCDM.

>>>>

\begin{abstract}
We use cosmological N-body simulations to find the characteristic mass
of dark matter halos hosting Lyman-Alpha Emitting (LAE) galaxies at a
redshift of $z=3.1$. The method is based on matching the statistics
for the number density between mock and observed fields. The mock
catalogs are constructed using a simple model where a dark matter halo
can only host one LAE with a probability $f_{\rm occ}$ if its mass is
found withing a certain range mass range delimited by two threshold
values, $M_{\rm min}$ and $M_{\rm max}$. We find that the most of the models that
are consistent the observed cosmic variance statistics are those with
halo masses in the range $10.5 < \log_{10} M_{\rm  min}/hMsun < 11.5$
and $\log_{10} M_{\rm max}/\hMsun < 13.5$ with and occupation fraction
that scales as $f_{\rm occ}=$. We explore three additional constraints
to narrow down these range: the number of mocks consistent with
observations, observational constraints on the occupation fraction and
the angular correlation function. The first two conditions narrow down
the space parameter to $M_{\rm min}=$ and $M_{\rm max}$, $f_{\rm occ}$. The angular
correlation function does not add a significant constraint due to the
cosmic variance in the small angular fields where this statistics has
been computed so far. We make available the mock data for the best
models in a public repository. Implications for galaxy formation
models? 
\end{abstract}

@@

Most models of galaxy formation find that the mass of the halo can be
used to predict properties of the galaxy such as its stellar mass and
star formation rate \citep{Behroozi2012}. Processes that regulate the
star formation cycle are also though to be strongly dependent on its
mass. Furthermore, the spatial clustering of galaxies on large scales
is entirely dictated by the halo distribution.  For the reasons
mentioned above, finding the typical dark matter halo mass hosting
LAEs represents a significant step forward to understand the nature of
this population in the context of Lambda Cold Dark Matter
($\Lambda$CDM) paradigm.
